### 2012-01-07 joint action and knowing others minds/interacting mindreaders.2.tex
added intention motor action (was svn, older revisions not imported but still in svn)

\documentclass[14pt,a4paper]{extarticle}
% extarticle is like article but can handle 8pt, 9pt, 10pt, 11pt, 12pt, 14pt, 17pt, and 20pt text

\def \ititle {Interacting Mindreaders}
\def \isubtitle {}
\def \iauthor {Stephen A. Butterfill}
\def \iemail{s.butterfill@warwick.ac.uk}
%\date{}

\input{$HOME/Documents/submissions/preamble_steve_paper2}

@@

\noindent
Word count: 10 200

@@

\section{A question about the evidential basis of mindreading}
\label{sec:intro}

@@

%Contrast this episode with an alternative where no distributive goal is involved.
%Instead of intending that we all pull up the enormous turnip,
%each of us intends that she herself pull it up.
%While all of our actions are directed to similar outcomes (they all involve pulling up the turnip),
%these are clearly different outcomes.
%They are clearly different because one could occur while another did not;
%one of us might have broken an arm and been unable to pullwhile the others succeeded.
%So in this case, freeing the turnip is not a distributive goal of our actions.
%For some actions to have a distributive goal,
%it is necessary that there be a single outcome (and not merely similar outcomes) to which they are directed.

@@

Is it ever possible to know the premises without first knowing the conclusion?  
Consider the first premise.  
Sometimes 
in the right contexts
an individual can recognize in another's facial expressions, engaging gestures or synchronized bodily movements that she is about to engage in joint action with her.
Exploiting these indicators does not typically depend on knowing the particular contents of any beliefs, desires or goals.  
Expressions, gestures and movements can naturally indicate imminent jointness in much the way thay can also naturally indicate emotions.\footnote{
Ideas along these lines are suggested by the discussion of {emergent coordination} in \citet{Knoblich:2010fk}.
}  
Of course these indicators provide no guarantee that others are genuinely willing to engage in joint action.  
But they are sufficiently reliable to ground knowledge in some cases.  
The existence of such indicators shows that knowing the first  premise of the above inference does not require already knowing which particular goals the other's actions will be directed to.

@@

The your-goal-is-my-goal
route to knowledge
sometimes enables mindreaders to avoid the problem of false belief.
To illustrate consider a counterfactual alternative to the above example.
Ayesha dislikes the owl and is concerned with retrieving the cat.
As you reach for the north box,
your facial gestures signal willingness to engage in joint action with Ayesha.
She then concludes, correctly, that your goal is her goal, to retrieve the cat.
So despite the difference in belief,
the possibility of interaction means that
Ayesha can knowledgably identify the goal of your action.

>>>>

\documentclass[12pt,a4paper]{extarticle}
% extarticle is like article but can handle 8pt, 9pt, 10pt, 11pt, 12pt, 14pt, 17pt, and 20pt text

\def \ititle {Interacting Mindreaders}
\def \isubtitle {}
%\def \iauthor {Stephen A. Butterfill}
%\def \iemail{s.butterfill@warwick.ac.uk}
\def \iauthor {}
\def \iemail{}
\date{}

\input{$HOME/Documents/submissions/preamble_steve_paper2}
\author{}

@@

%\noindent
%Word count: 10 100

@@

\section{On the evidential basis of mindreading}
\label{sec:intro}

@@

%Contrast this episode with an alternative where no distributive goal is involved.
%Instead of intending that we all pull up the enormous turnip,
%each of us intends that she herself pull it up.
%While all of our actions are directed to similar outcomes (they all involve pulling up the turnip),
%these are clearly different outcomes.
%They are clearly different because one could occur while another did not;
%one of us might have broken an arm and been unable to pull while the others succeeded.
%So in this case, freeing the turnip is not a distributive goal of our actions.
%For some actions to have a distributive goal,
%it is necessary that there be a single outcome (and not merely similar outcomes) to which they are directed.

@@

Is it ever possible to know the premises without first knowing the conclusion?  
Consider the first premise.  
Sometimes 
in the right contexts
an individual can recognize in another's facial expressions, engaging gestures or synchronized bodily movements that she is about to engage in joint action with her.
Exploiting these indicators does not typically depend on knowing the particular contents of any beliefs, desires or goals.  
Expressions, gestures and movements can naturally indicate imminent jointness in much the way they can also naturally indicate emotions.\footnote{
Ideas along these lines are suggested by the discussion of {emergent coordination} in \citet{Knoblich:2010fk}.
}  
Of course these indicators provide no guarantee that others are genuinely willing to engage in joint action.  
But they are sufficiently reliable to ground knowledge in some cases.  
The existence of such indicators shows that knowing the first  premise of the above inference does not require already knowing which particular goals the other's actions will be directed to.

@@

The your-goal-is-my-goal
route to knowledge
sometimes enables mindreaders to avoid the problem of false belief.
To illustrate consider a counterfactual alternative to the above example.
Ayesha dislikes the owl and is concerned with retrieving the cat.
As you reach for the north box,
your facial gestures signal willingness to engage in joint action with Ayesha.
She then concludes, correctly, that your goal is her goal, to retrieve the cat.
So despite the difference in belief,
the possibility of interaction means that
Ayesha can knowledgeably identify the goal of your action.
